\documentclass{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}

\begin{document}
\title{Vacation Sheet 8}
\author{Ben Eills}
\maketitle

\textit{Submit neat answers to all the questions you attempt (include all the working you wish to be marked, e.g. calculations, diagrams).  Partial answers should also be handed in: these may be awarded partial credit.  Try to complete the questions at an examination pace; time yourself!}

\begin{enumerate}
	\item Given that $y = 3x^7 - 1 + x^{\frac{1}{2}}$ for $x > 0$ \\
			Find $\dfrac{dy}{dx}$
	
	
	\item 
	
		\begin{enumerate}
			\item Express $\sqrt{147}$ in the "surd form" $a \sqrt{3}$, where a is an integer.
			
			\item Express $(7 - \sqrt{5})^2$ in the "surd form" $a + b \sqrt{3}$, where a and b are integers.	
			
			\item Express $36 - 16 \sqrt{5}$ in the form $(a - b \sqrt{5})^2$, where a and b are integers.
		\end{enumerate}


	\item Let $f(x) = \dfrac{1}{x}$
	
		\begin{enumerate}
			\item Sketch $4f(x) + 3$, marking all intersections and asymptotes.
			
			\item Give the equations of all asymptotes.
			
			\item Find both $\dfrac{df}{dx}$ and $\dfrac{d}{dx} (4f(x) + 3)$
		\end{enumerate}

	
	\item Consider the two straight lines defined by:
			$$ 3x + 5y = 12 $$
			$$ 2x + 10y = 7 $$
			
		\begin{enumerate}
			\item Sketch them both and convince yourself that they intersect (i.e. are not parallel)
			
			\item Solve the system of equations algebraically.
			
			\item What is the area of the triangle bounded by the two lines and the y-axis?
		\end{enumerate}
	
	\item The quadratic $3x^2 - 5x + (k+2)$ has no real roots.
		\begin{enumerate}
			\item Give the range of possible values for k.
			
			\item Sketch the graph, giving the value of the y-intercept (in terms of k).
		\end{enumerate}
	
	\item Find
			$$ \int (2 - 7 \sqrt{2})^2 dx$$
	
	\item Given that a curve has equation $y = f(x)$, passes through the point \\ $P=(2, 7)$, and satisfies
			$$f'(x) = 3x^2 - 4$$
			Find and sketch $f(x)$.
\end{enumerate}

\end{document}